A Critical Appraisal of Zero-Multiple Method in Simulation Biomolecular Systems

### 2014-09-11 writedown/zm/group.nlist/cutoff.tex
backup

>>>>

A looser condition can be considered. Since only 0.16\% of the molecules
has velocity larger than 5~nm/ps at a certain time frame, the velocity can be
roughly bounded by  5~nm/ps.
If the neighbor list is updated every 10 time-steps, 
$d_{COG}$ is estimated to be roughly bounded $0.001 \times 10 \times 5 = 0.05$~nm.
We can set  $\rlist - \rcoulomb = 0.26$~nm, then we need $d_{COG} < 0.052\ \textrm{nm}$, which is satisfied.

### 2014-09-11 writedown/zm/report/report.tex
backup

\subsubsection{Pressure}
The results are plotted in Fig.~\ref{fig:tmp0}. All pressure calculations are done with system $\systemla$.
\begin{figure}
  \centering
  \includegraphics[]{pressure-methods.eps}
  \caption{The pressure convergence with respect to the cut-off radius.
    For ZM method, the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
  }
  \label{fig:tmp0}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[]{fig-gkr-small.eps}
  \includegraphics[]{fig-gkr-small-conv.eps}
  \includegraphics[]{fig/result.nvt.small/fig-eps-t-3000.eps}
  \includegraphics[]{fig/result.nvt.small/fig-eps-t-zm3-3000.eps}
  \includegraphics[]{fig/result.nvt.small/fig-eps-t-10000.eps}
  \includegraphics[]{fig/result.nvt.small/fig-eps-t-zm3-10000.eps}
  \caption{The Kirkwood G-factor calculated for system $\systemmb$.
    % The result of different methods are compared in the left plot.
    For all ZM methods the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
    In the left plot the cut-off radius for all orders is set to $1.2$~nm, while
    in the right plot, only the order $l=3$ is considered and different cut-off radii are compared.
    The RF method uses a cut-off radius of 1.2~nm, and dielectric constant of 80.
    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red bar.
  }
  \label{fig:tmp1}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[]{fig-gkr.eps}
  \includegraphics[]{fig-gkr-conv.eps}
  \includegraphics[]{fig/result.nvt/fig-eps-t-3000.eps}
  \includegraphics[]{fig/result.nvt/fig-eps-t-zm3-3000.eps}
  \caption{The Kirkwood G-factor calculated for system $\systemlb$.
    % The result of different methods are compared in the left plot.
    For all ZM methods the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
    In the left plot the cut-off radius for all orders is set to $1.2$~nm, while
    in the right plot, only the order $l=3$ is considered and different cut-off radii are compared.
    The RF method uses a cut-off radius of 1.2~nm, and dielectric constant of 80.
    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red bar.
  }
  \label{fig:tmp2}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[]{fig-gkr-10000.eps}
  \includegraphics[]{fig-gkr-conv-10000.eps}
  \includegraphics[]{fig/result.nvt/fig-eps-t-10000.eps}
  \includegraphics[]{fig/result.nvt/fig-eps-t-zm3-10000.eps}
  \caption{The Kirkwood G-factor calculated for system $\systemlb$. Equilibriation time is 10~ns, and the production simulation time is 10~ns.
    % The result of different methods are compared in the left plot.
    For all ZM methods the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
    In the left plot the cut-off radius for all orders is set to $1.2$~nm, while
    in the right plot, only the order $l=3$ is considered and different cut-off radii are compared.
    The RF method uses a cut-off radius of 1.2~nm, and dielectric constant of 80.
    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red bar.
  }
  \label{fig:tmp3}
\end{figure}

@@

We simulate the alanine dipeptide with the Amber
ff-99SB-ILDN~\cite{lindorff2010improved} force field.  The dihedral
angles $\phi$ and $\psi$ (see Fig.~\ref{fig:free-energy}~(a)) are
widely accepted as collective variables that can describe the
conformational dynamics of the system.  The free energy landscape
on $\phi$-$\psi$ space is given in Fig.~\ref{fig:free-energy}~(b).  The projected
probability distributions on both dihedral angles
with error bars are presented in Fig.~\ref{fig:dih-dist}. It can be easily seen
from the distribution $P(\psi)$ and $P(\psi)$ that the ZM method with
$l=2$ and 3 reproduce the over-all probability of the main
conformations, i.e.~the $\alpha$-helix (right-handed), $\beta$-sheet and
the left-handed $\alpha$-helix with satisfactory accuracy.  For these
methods, deviations of $P(\phi)$ at $\phi = -75^\circ$ and $\phi =
-140^\circ$ are observed. They correspond to the double-peak structure
of the right-handed $\alpha$-helix and $\beta$-sheet, which means the
error happens at the sub-structure of the right-handed $\alpha$-helix
and $\beta$-sheet, which are of relatively smaller biological interest
comparing with the main conformations.

\begin{table}
  \centering
  \caption{The first three non-trivial timescales in ps computed at lag-time $\tau = 20$~ps.
  }
  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}c   ccc}\hline\hline
    Method      &        $t_2$ [ps]  & $t_3$ [ps] &  $t_4$ [ps] \\\hline
    SPME        &         1292  (148)     &          69.95  (0.76)  &         36.0 (4.7)    \\
    RF          & \textbf{1615} (155)     &  \textbf{68.48} (0.37)  &         34.1 (1.6)    \\
    ZM $l=1$    & \textbf{1607} (218)     &  \textbf{72.08} (0.50)  &         31.4 (1.9)    \\
    ZM $l=2$    &         1324  (110)     &          69.97  (0.58)  &         40.4 (2.8)    \\
    ZM $l=3$    &         1312  (157)     &          70.50  (0.72)  &         37.1 (4.3)    \\
    ZM $l=4$    & \textbf{1635} (156)     &          69.71  (0.54)  &         39.2 (3.6)    \\
    \hline\hline
  \end{tabular*}
  \label{tab:tmp3}
\end{table}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-2.eps}
  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-2.eps}
  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-2.eps}
  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-2.eps}
  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-2.eps}\\
  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-3.eps}
  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-3.eps}
  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-3.eps}
  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-3.eps}
  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-3.eps}\\
  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-4.eps}
  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-2-comp.eps}
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-3-comp.eps}
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-4-comp.eps}\\
  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-4.eps}
  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-5.eps}\\
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-2-comp.eps}
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-3-comp.eps}
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-4-comp.eps}
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-5-comp.eps}\\
  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-4.eps}\\
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-5.eps}\\
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-spme-eig-vec-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-2.eps}\\
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-spme-eig-vec-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-3.eps}\\
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-spme-eig-vec-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-4.eps}
  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-2-comp.eps}
  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-3-comp.eps}
  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-4-comp.eps}\\
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-4.eps}
  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-5.eps}\\
  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-2-comp.eps}
  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-3-comp.eps}
  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-4-comp.eps}
  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-5-comp.eps}\\
  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-4.eps}\\
  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-5.eps}\\
  \caption{The eigenfunctions corresponding to the largest three
    non-trivial timescales, computed with lag-time 20~ps.}
  \label{fig:tmp5}
\end{figure}

>>>>

\subsubsection{Pressure}
The results are plotted in Fig.~\ref{fig:tmp0}. All pressure calculations are done with system $\systemla$.
\begin{figure}
  \centering
  \includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
  \caption{The pressure convergence with respect to the cut-off radius.
    For ZM method, the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
  }
  \label{fig:tmp0}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[]{fig/result.nvt.small/fig-gkr-small.eps}
  \includegraphics[]{fig/result.nvt.small/fig-gkr-small-conv.eps}
  \includegraphics[]{fig/result.nvt.small/fig-eps-t-3000.eps}
  \includegraphics[]{fig/result.nvt.small/fig-eps-t-zm3-3000.eps}
  \includegraphics[]{fig/result.nvt.small/fig-eps-t-10000.eps}
  \includegraphics[]{fig/result.nvt.small/fig-eps-t-zm3-10000.eps}
  \caption{The Kirkwood G-factor calculated for system $\systemmb$.
    % The result of different methods are compared in the left plot.
    For all ZM methods the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
    In the left plot the cut-off radius for all orders is set to $1.2$~nm, while
    in the right plot, only the order $l=3$ is considered and different cut-off radii are compared.
    The RF method uses a cut-off radius of 1.2~nm, and dielectric constant of 80.
    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red bar.
  }
  \label{fig:tmp1}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[]{fig/result.nvt/fig-gkr.eps}
  \includegraphics[]{fig/result.nvt/fig-gkr-conv.eps}
  \includegraphics[]{fig/result.nvt/fig-eps-t-3000.eps}
  \includegraphics[]{fig/result.nvt/fig-eps-t-zm3-3000.eps}
  \caption{The Kirkwood G-factor calculated for system $\systemlb$.
    % The result of different methods are compared in the left plot.
    For all ZM methods the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
    In the left plot the cut-off radius for all orders is set to $1.2$~nm, while
    in the right plot, only the order $l=3$ is considered and different cut-off radii are compared.
    The RF method uses a cut-off radius of 1.2~nm, and dielectric constant of 80.
    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red bar.
  }
  \label{fig:tmp2}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[]{fig/result.nvt/fig-gkr-10000.eps}
  \includegraphics[]{fig/result.nvt/fig-gkr-conv-10000.eps}
  \includegraphics[]{fig/result.nvt/fig-eps-t-10000.eps}
  \includegraphics[]{fig/result.nvt/fig-eps-t-zm3-10000.eps}
  \caption{The Kirkwood G-factor calculated for system $\systemlb$. Equilibriation time is 10~ns, and the production simulation time is 10~ns.
    % The result of different methods are compared in the left plot.
    For all ZM methods the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
    In the left plot the cut-off radius for all orders is set to $1.2$~nm, while
    in the right plot, only the order $l=3$ is considered and different cut-off radii are compared.
    The RF method uses a cut-off radius of 1.2~nm, and dielectric constant of 80.
    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red bar.
  }
  \label{fig:tmp3}
\end{figure}

@@

We simulate the alanine dipeptide with the Amber
ff-99SB-ILDN~\cite{lindorff2010improved} force field.  The dihedral
angles $\phi$ and $\psi$ (see Fig.~\ref{fig:free-energy}~(a)) are
widely accepted as collective variables that can describe the
conformational dynamics of the system.  The free energy landscape
on $\phi$-$\psi$ space is given in Fig.~\ref{fig:free-energy}~(b).  The projected
probability distributions on both dihedral angles
with error bars are presented in Fig.~\ref{fig:dih-dist}. It can be easily seen
from the distribution $P(\psi)$ and $P(\psi)$ that the ZM method with
$l=2$ and 3 reproduce the over-all probability of the main
conformations, i.e.~the $\alpha$-helix (right-handed), $\beta$-sheet and
the left-handed $\alpha$-helix with satisfactory accuracy.
% For these
% methods, deviations of $P(\phi)$ at $\phi = -75^\circ$ and $\phi =
% -140^\circ$ are observed. They correspond to the double-peak structure
% of the right-handed $\alpha$-helix and $\beta$-sheet, which means the
% error happens at the sub-structure of the right-handed $\alpha$-helix
% and $\beta$-sheet, which are of relatively smaller biological interest
% comparing with the main conformations.

\begin{table}
  \centering
  \caption{The first three non-trivial timescales in ps computed at lag-time $\tau = 20$~ps.
  }
  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}c   ccc}\hline\hline
    Method      &        $t_2$ [ps]  & $t_3$ [ps] &  $t_4$ [ps] \\\hline
    SPME        &         1374  (235)     &          70.03  (0.64)  &         39.2  (4.3)    \\
    RF          &        {1615} (177)     &  \textbf{68.49} (0.42)  & \textbf{34.1} (2.2)    \\
    ZM $l=1$    &        {1244} (099)     &         {71.00} (0.46)  &         36.2  (4.4)    \\
    ZM $l=2$    &         1407  (194)     &          70.46  (0.76)  &         38.7  (2.4)    \\
    ZM $l=3$    &         1449  (116)     &          70.20  (0.57)  &         37.4  (2.5)    \\
    ZM $l=4$    &        {1119} (129)     &          70.05  (0.71)  &         34.6  (1.8)    \\
    \hline\hline
  \end{tabular*}
  \label{tab:tmp3}
\end{table}

@@

% \begin{figure}
%   \centering
%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-2.eps}
%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-2.eps}
%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-2.eps}
%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-2.eps}
%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-2.eps}\\
%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-3.eps}
%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-3.eps}
%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-3.eps}
%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-3.eps}
%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-3.eps}\\
%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-4.eps}
%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-4.eps}
%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-4.eps}
%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-4.eps}
%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-4.eps}\\
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-5.eps}\\
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-2-comp.eps}
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-3-comp.eps}
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-4-comp.eps}\\
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-2-comp.eps}
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-3-comp.eps}
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-4-comp.eps}\\
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-2-comp.eps}
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-3-comp.eps}
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-4-comp.eps}\\
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-5-comp.eps}\\
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-5.eps}\\
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-spme-eig-vec-2.eps}
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-2.eps}
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-2.eps}
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-2.eps}\\
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-spme-eig-vec-3.eps}
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-3.eps}
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-3.eps}
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-3.eps}\\
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-spme-eig-vec-4.eps}
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-4.eps}
%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-2-comp.eps}
%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-3-comp.eps}
%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-4-comp.eps}\\
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-4.eps}
%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-5.eps}\\
%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-2-comp.eps}
%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-3-comp.eps}
%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-4-comp.eps}
%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-5-comp.eps}\\
%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-4.eps}\\
%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-5.eps}\\
%   \caption{The eigenfunctions corresponding to the largest three
%     non-trivial timescales, computed with lag-time 20~ps.}
%   \label{fig:tmp5}
% \end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.24\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-2.eps}
  \raisebox{.35cm}{\includegraphics[width=0.21\textwidth]{fig/result.alanine.amber/fig-eig-vec-error-2-phi.eps}}
  \raisebox{.35cm}{\includegraphics[width=0.21\textwidth]{fig/result.alanine.amber/fig-eig-vec-error-2-psi.eps}}\\
  \includegraphics[width=0.24\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-3.eps}
  \raisebox{.35cm}{\includegraphics[width=0.21\textwidth]{fig/result.alanine.amber/fig-eig-vec-error-3-phi.eps}}
  \raisebox{.35cm}{\includegraphics[width=0.21\textwidth]{fig/result.alanine.amber/fig-eig-vec-error-3-psi.eps}}\\
  \includegraphics[width=0.24\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-4.eps}
  \raisebox{.35cm}{\includegraphics[width=0.21\textwidth]{fig/result.alanine.amber/fig-eig-vec-error-4-phi.eps}}
  \raisebox{.35cm}{\includegraphics[width=0.21\textwidth]{fig/result.alanine.amber/fig-eig-vec-error-4-psi.eps}}\\
  \caption{The eigenfunctions corresponding to the largest three
    non-trivial timescales, computed with lag-time 20~ps.  The left
    colume shows the eigenfunctions computed by SPME method. The right colume
    shows the deviation of RF, ZM ($l=1,\cdots,4$) with respect to
    SPME.  To present the statistical uncertainty, the second
    eigenfunction is projected on to dihedral angle $\phi$, while the
    third and fourth eigenfunctions are projected on $\psi$.  The red
    shadow region presents the statistical uncertainty of SPME. For
    clarity, only the statistical uncertainty of RF and ZM $l=3$ are
    presented by error bars.  }
  \label{fig:tmp5}
\end{figure}
